Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

\section{Expectation Values for IVPMs\label{sec:ExpectationValue}}

We may need to understand how to define expectation values of an observable
for quantum IVPMs. Recall an observable is the quantum version of
a random variable. Hence, in order to define expectation values of
an observable, we need to understand the definition of expectation
values of a random variable for an classical IVPM.

>>>>

\section{Expectation Values for IVPMs}

We may need to understand how to define expectation values of an observable
for quantum IVPMs. Recall an observable is the quantum version of
a random variable. Hence, in order to define expectation values of
an observable, we need to understand the definition of expectation
values of a random variable for an classical IVPM. Since the expectation
value of random variable~$X$ is the integral $\int X\rmd\pmeas$~\cite{Kolmogorov1950},
we need to understand the meaning of integration on IVPMs. In the
rest of the section, we will consider the real-valued and interval-valued
probability measure defined in example~\ref{ex1} and \ref{ex3},
and see how to compute the expectation value of different random variables.
